Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-22 main.tex
Forgot to note that process noise is zero mean
Updated biography to suit new affiliation

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reduce communication to the protocol above, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate captures the navigator position, and the change in position ($\Delta$), and is given by
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & \Delta x & y & \Delta y
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
The state evolves following a known system model, which at timestep $k$ is given by
\begin{equation}
    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
\end{equation}
with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_{k,i})$ and measurement function
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,,
    \end{split}
\end{equation}
where
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top
\end{equation} 
is the location of sensor $i$.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
received his software engineering diploma in 2018 at the University of Melbourne, Australia. Since 2019, he has been pursuing a Ph.D. at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany. His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed filtering.
\end{IEEEbiography}

>>>>

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reduce communication to the protocol above, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate captures the navigator position, and the change in position ($\Delta$), and is given by
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & \Delta x & y & \Delta y
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
The state evolves following a known system model, which at timestep $k$ is given by
\begin{equation}
    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
\end{equation}
with system noise that is zero mean and has covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_{k,i})$ and measurement function
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,,
    \end{split}
\end{equation}
where
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top
\end{equation} 
is the location of sensor $i$.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
received his software engineering diploma in 2018 at the University of Melbourne, Australia. In 2019, he began work as a researcher at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany, and since 2021, he has been pursuing a Ph.D. at the Autonomous Multisensor Systems (AMS) group, Otto von Guericke University, Germany. His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed localisation.
\end{IEEEbiography}
